Semi-permeable vesicles: mathematical formulation, numerics and physics

### 2020-04-23 vesicle_code/docs/permeableVes/main.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear Flow}
\begin{itemize}
  \item Never goes to a circle
  \item Area formula works
  \item Mild dependence on initial shape
  \item Most slender tank treading shapes seen for small $\beta$ and
    large $\chi$
\end{itemize}

@@

\ifTikz
\input{figures/shearPhaseDiagram.tikz}
\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poiseuille Flow}
\begin{itemize}
  \item ???
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear Flow}
\begin{itemize}
  \item Never goes to a circle
  \item Area formula works
  \item Mild dependence on initial shape
  \item Most slender tank treading shapes seen for small $\beta$ and
    large $\chi$

  \item Look at tank-treading angle, tank-trading speed, reduced area,
    absolute value of the permeable flux
  \item Max flux at the steady state as a function of beta and
    $\dot{\gamma}$

  \item reduced area/inclination angle for a particular $(\beta,\gamma)$
    and different flux rates using the gating functions (Apr 7 and 9) as
    well as constant $\beta$
\end{itemize}

@@

%\ifTikz
\input{figures/shearPhaseDiagram.tikz} 
%\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poiseuille Flow}
\begin{itemize}
  \item Does permeability affect the rate of migration
\end{itemize}
